Reproducible and Programmatic Generation of Neuroimaging Visualizations

### 2022-08-15 readme.Rmd
rd up
tabel added to rdme

c.	Chopra, S., Labache, L., Dhamala, E., Orchard, E., Holmes. A. [Reproducible and programmatic generation of neuroimaging visualizatio](https://github.com/sidchop/RepoNeuroVis/blob/main/manuscript.pdf). Preprint.

@@

>>>>

**Chopra, S.**, Labache, L., Dhamala, E., Orchard, E., Holmes. A. [Reproducible and programmatic generation of neuroimaging visualizatio](https://github.com/sidchop/RepoNeuroVis/blob/main/manuscript.pdf). Preprint.

@@

## Examples of code-based neuroimaging visualizations tools that can be accessed directly within R, MATLAB and Python environments.

|                                                        | Voxel   | Vertex  | ROI           | Edge    | Streamlines |
|:-----------|:-----------|:-----------|:-----------|:-----------|:-----------|
| **R**                                                  |         |         |               |         |             |
| [ANTsR](https://github.com/ANTsX/ANTsR)                | ***+*** | ***+*** | ***+***       |         |             |
| [brainconn](https://github.com/sidchop/brainconn)      |         |         |               | ***+*** |             |
| [brainR](https://github.com/muschellij2/brainR)        | ***+*** |         | ***+***       |         |             |
| [ciftitools](https://github.com/mandymejia/ciftiTools) | ***+*** | ***+*** | ***+*****\*** |         |             |
| [fsbrain](https://github.com/dfsp-spirit/fsbrain)      | ***+*** | ***+*** | ***+*****\*** |         |             |
| ggseg                                                  |         |         | ***+***       |         |             |
| neurobase                                              | ***+*** |         |               |         |             |
| oro.nifti                                              | ***+*** |         |               |         |             |
| **Python**                                             |         |         |               |         |             |
| ANTsPy                                                 | ***+*** | ***+*** | ***+***       |         |             |
| brainiak                                               | ***+*** |         |               |         |             |
| Brainplotlib                                           |         | ***+*** | ***+*****\*** |         |             |
| Brainspace/surfplot                                    |         | ***+*** | ***+*****\*** |         |             |
| DIPY                                                   | ***+*** |         |               |         | ***+***     |
| ENIGMA toolbox                                         |         |         | ***+***       |         |             |
| FSLeyes                                                | ***+*** | ***+*** | ***+***       |         |             |
| ggseg                                                  |         |         | ***+***       |         |             |
| graphpype                                              |         |         |               | ***+*** |             |
| MMVT                                                   |         | ***+*** | ***+***       | ***+*** |             |
| MNE                                                    | ***+*** | ***+*** | ***+***       |         |             |
| mrivis                                                 | ***+*** |         |               |         |             |
| NaNSlice                                               | ***+*** |         |               |         |             |
| netneurotools                                          |         | ***+*** | ***+*****\*** |         |             |
| nilearn                                                | ***+*** | ***+*** | ***+***       | ***+*** |             |
| niwidget                                               | ***+*** | ***+*** |               |         | ***+***     |
| Pycortex                                               | ***+*** | ***+*** | ***+*****\*** |         |             |
| pySurfer                                               |         | ***+*** | ***+*****\*** |         |             |
| surfice                                                | ***+*** | ***+*** | ***+***       | ***+*** | ***+***     |
| surfplot                                               |         | ***+*** | ***+***       |         |             |
| Visbrain                                               | ***+*** | ***+*** | ***+***       | ***+*** |             |
| **MATLAB**                                             |         |         |               |         |             |
| BrainNetViewer                                         | ***+*** |         | ***+***       | ***+*** |             |
| Brainspace                                             |         | ***+*** | ***+*****\*** |         |             |
| Brainstorm                                             | ***+*** | ***+*** | ***+***       |         |             |
| bspmview                                               | ***+*** |         | ***+***       |         |             |
| CandlabCore                                            | ***+*** |         | ***+***       |         |             |
| ECoG/fMRI Vis toolbox                                  |         | ***+*** | ***+*****\*** |         |             |
| ENIGMA toolbox                                         |         |         | ***+***       |         |             |
| FieldTrip                                              | ***+*** | ***+*** |               |         |             |
| Lead-DBS                                               | ***+*** |         | ***+***       |         |             |
| mni2fs                                                 |         | ***+*** |               |         |             |
| mrtools                                                | ***+*** | ***+*** | ***+*****\*** |         |             |
| plotSurfaceROIBoundary                                 |         | ***+*** | ***+*****\*** |         |             |
| Vistasoft                                              | ***+*** | ***+*** | ***+***       |         | ***+***     |

Note: The tools listed contain functionality required to generate (at least close-to) publication-ready neuroimaging figures via user-entered code within R, MATLAB and Python environments. This list does not include cross-platform general purpose visualization software.\
\*Cortex only
